---
title: "Reproduction of 'Newspapers in Times of Low Advertising Revenues' by Charles Angelucci and Julia Cagé"
author: "Yitian Zhao"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: |
  | With the rise of the internet and a shift in consumer behaviour headed towards digital platforms, the newspaper industry is worried about its ability to produce high-quality journalism with the decrease in advertising revenue. We are looking to recreate and investigate the findings of Charles Angelucci and Julia Cagé in their paper as they construct a dataset analyzing the effects on the French newspaper industry as advertising shifts towards French television between 1960 to 1974. We see that this a nearly parallel shift with the digitalization of advertising today as only the newspapers ad revenue is directly impacted while their costs, productivity, and readership remain under their control. As the study reveals that newspapers ended up playing a smaller role in delivering significant journalistic content in the 1960s, it goes into question how the industry will keep afloat as income keeps decreasing and journalism shifts towards other platforms.
  |
  | **Keywords: newspaper advertising, advertising revenue, ordinary least squares regression, journalism** 
thanks: "Code and data are available here at: https://github.com/ytz1211/sta304_ps5"

output:
  bookdown::pdf_document2:
toc: FALSE
nocite: '@*'
link-citations: yes
---

```{r setup, include=FALSE}
library(here)
library(haven)
library(huxtable)
library(scales)
library(tidyverse)
library(dplyr)
# Read in datasets
Micro_dataset <- (read_dta("116438-V1/data/dta/Angelucci_Cage_AEJMicro_dataset.dta"))
Micro_Descriptive_evidence_advertisement <- (read_dta("116438-V1/data/dta/Angelucci_Cage_AEJMicro_Descriptive_evidence_advertisement.dta"))
Micro_Descriptive_evidence_advertising_industry <- (read_dta("116438-V1/data/dta/Angelucci_Cage_AEJMicro_Descriptive_evidence_advertising_industry.dta"))
Micro_Descriptive_evidence_television_quality <- (read_dta("116438-V1/data/dta/Angelucci_Cage_AEJMicro_Descriptive_evidence_television_quality.dta"))
Micro_Descriptive_evidence_US <- (read_dta("116438-V1/data/dta/Angelucci_Cage_AEJMicro_Descriptive_evidence_US.dta"))

```

# Introduction

Inspired by Charles Angelucci and Julia Cagé's "Newspapers in Times of Low Advertising Revenues", we are looking to recreate their results investigating the effects on journalist employment, news quantity, and newspapers pricing that a lowered advertising revenue has on both national and local French newspaper companies. 

In the modern time period where the Internet and social media dominate as news platforms, we are interested in how changing consumer preferences and productivity due to digitalization has overall negatively impacted the newspapers industry. Factors such as how advertisers are generally moving towards online platforms away from newspapers impact revenue generated from ads within the market and the shift in the income fundamentally requires a refocus in costs for newsrooms and journalists if the industry hopes to survive. The framework in which these relationships are analyzed is through a model where a newspaper is in control of price rates with both advertisers and its reader audience. It is taken into account that different readers prefer different amounts and variety of journalistically intensive content and that the journalistic content written has a direct positive correlation to costs for the newspaper. This framework allows for the analysis of how these factors come into play ultimately with advertising revenue as well as each other. It predicts that a decrease in advertising revenue leads to a shift in the content and readerbase where less journalistically intensive content is produced and the newspaper price drops catered towards an audience less focused on significant and meaningful news.

It is not the first time that the newspaper industry has had to compete with sources of news moving to a more advanced technological platform. We follow Angelucci and Cagé's method to investigate how the predictions hold up against datasets built from information on French local and national newspapers and television between 1960 to 1974. As this time period was when technological advancements made it viable for televisions to be mass produced and affordable for families, it raised the opportunity for advertising companies to move to another platform and focus their efforts there which meant less resources invested into conventional newspaper ads. The introduction of television ads did not directly impact the costs and productivity of the newspaper industry as they only directly affected the advertising portion which provides a similar setting where cost, productivity, and readership is still under the control of the newspaper companies and will likely be reorganized in order to address a decreasing advertising revenue. 

# Data

The data we are using is the same data collected by Angelucci and Cagé which is a data set on national and local French newspapers taken from 1960 to 1974. This is newspaper data that they have gathered from various historical sources that is now compiled into a digital format.

The information on prices, revenues, and circulation was collected from the French Ministry of Information’s records
in the National archives as they required newspapers to report annually their revenues and prices. It is here where the information on the unit price, subscription price (annual subscription price divided by number of issues within the year), advertising revenues, sales revenues, number of issues, and information on circulation of unit buyers and subscription buyers is found. Their data set consists of samples of 68 local daily newspaper companies and 12 national daily newspaper companies. These samples represent a large portion of the local newspaper industry and the entire national newspaper industry during that time period.

Data on the journalists themselves was collected through “Commission de la carte d’identité des journalistes professionnels” (CCIJP) which is the organization that issues press cards to journalists. According to French regulations, media companies are not allowed to employ professional journalists without press cards for longer than 3 months. Journalists must also renew their press card annually. Data for this category was collected for 63/68 of the local newspapers and 11/12 of the national newspapers. Journalist information includes the number of journalists at a given newspaper company per year and their monthly salary. Data on journalists working for the French television and radio broadcasting agency (ORTF) was also collected for the years 1960, 1964-1971, and 1974. Similar to newspaper journalists, television journalists also require a press card to be employed.

Advertising revenues are affected by changing advertising prices and/or changing advertising quantities. Data is collected for both of these factors as we hope to see the effects of both on revenue. According to Angelucci and Cagé, the main source for gathering information on advertising prices is the official list price per column inch of advertising space from “Tarif Media,” an annual publication that provides information regarding advertising rates. As rates differ depending on the page which an ad is placed, the single rate they decided to use is for front page ads only as they have the most observations for it. A disadvantage of this method is that the rates are frequently discounted so the actual transaction price is lower. To combat this, another source of measuring prices comes from taking the total advertising revenue to be divided by the newspaper circulation. The amount of ads per issue comes from copies available in the French National Library providing the total number of ads and proportion of ads in the newspaper.

By investigating the newspapers' contents, Angelucci and Cagé were also able to determine the amount of space dedicated to news. Changes in the content were analyzed through in 37 of the local newspapers and all of the national newspapers in the sample. The share of hard news and soft news stories were computed in each annual March issue in the 3rd week from 1964 to 1972.

Taking information from the Centre d’Etude des Supports de Publicité (CESP), Angelucci and Cagé were able to obtain data on readers' characteristics. The CESP is an organization comprised of the biggest advertising businesses and thye produce reports on newspaper readers every 5 years from 1957 to 1967 and yearly beginning 1968. Data on their survey responses is included for the years 1957, 1962, 1967-1970, 1972, and 1974.


# Model

```{r, echo=FALSE}

newspapers <- Micro_dataset
newspapers <- mutate(newspapers, ra_cst_div_qtotal = ra_cst / qtotal) 
newspapers <- mutate_at(newspapers, vars(id_news, after_national, local, national), ~as.factor(.))
newspapers <- mutate(newspapers, year = as.integer(year))


# Advertising side
ad_revenue <- lm(log(ra_cst) ~ after_national + id_news + year, data = newspapers)
ad_revenue_div_circulation <- lm(log(ra_cst_div_qtotal) ~ after_national + id_news + year, data = newspapers)
ad_price <- lm(log(ads_p4_cst) ~ after_national + id_news + year, data = newspapers)
ad_space <- lm(log(ads_s) ~ after_national + id_news + year, data = newspapers)

# Consumer side
subscription_price <- lm(log(ps_cst) ~ after_national + id_news + year, data = newspapers)
unit_price <- lm(log(po_cst) ~ after_national + id_news + year, data = newspapers)
circulation <- lm(log(qtotal) ~ after_national + id_news + year, data = newspapers)
share_of_sub <- lm(log(qs_s) ~ after_national + id_news + year, data = newspapers)
revenue_from_sales <- lm(log(rs_cst) ~ after_national + id_news + year, data = newspapers)

omit_me <- c("(Intercept)", "id_news3", "id_news6", "id_news7", "id_news13", 
             "id_news16", "id_news25", "id_news28", "id_news34", "id_news38", 
             "id_news44", "id_news48", "id_news51", "id_news53", "id_news54", 
             "id_news57", "id_news60", "id_news62", "id_news66", "id_news67", 
             "id_news70", "id_news71", "id_news72", "id_news80", "id_news82", 
             "id_news88", "id_news95", "id_news97", "id_news98", "id_news103", 
             "id_news105", "id_news106", "id_news118", "id_news119", "id_news127", 
             "id_news136", "id_news138", "id_news148", "id_news151", "id_news153", 
             "id_news154", "id_news157", "id_news158", "id_news161", "id_news163", 
             "id_news167", "id_news169", "id_news179", "id_news184", "id_news185", 
             "id_news187", "id_news196", "id_news206", "id_news210", "id_news212", 
             "id_news213", "id_news224", "id_news225", "id_news234", "id_news236", 
             "id_news245", "id_news247", "id_news310", "id_news452", "id_news467", 
             "id_news469", "id_news480", "id_news20040", "id_news20345", 
             "id_news20346", "id_news20347", "id_news20352", "id_news20354", 
             "id_news21006", "id_news21025", "id_news21173", "id_news21176", 
             "id_news33718", "id_news34689", "id_news73")
print("Table 1")
huxreg("Subscription price" = subscription_price, 
       "Unit price" = unit_price, 
       "Circulation" = circulation, 
       "Share of sub" = share_of_sub,
       "Revenue from sales" = revenue_from_sales,
       omit_coefs = omit_me, 
       number_format = 2
       )

print("Table 2")
huxreg("Ad. rev." = ad_revenue, 
       "Ad rev. div. circ." = ad_revenue_div_circulation, 
       "Ad price" = ad_price, 
       "Ad space" = ad_space,
        omit_coefs = omit_me, 
        number_format = 2
        )
```

Our OLS model equation is: 

\begin{equation}
ln(y_{n,t}) = \beta_0 + \beta_1(National Dummy * 1967 Onward Dummy) + \lambda_n + \gamma_y + e
\end{equation}



# Results



# Discussion

# References

- R Core Team (2020). R: A language and environment for statistical computing. R, Foundation for Statistical Computing,   Vienna, Austria. URL, https://www.R-project.org/.

- Wickham et al., (2019). Welcome to the tidyverse. Journal of Open Source Software, 4(43), 1686,    https://doi.org/10.21105/joss.01686

- Hadley Wickham and Evan Miller (2020). haven: Import and Export 'SPSS', 'Stata' and 'SAS' Files. R package
  version 2.3.1. https://CRAN.R-project.org/package=haven

- Hadley Wickham, Romain François, Lionel Henry and Kirill Müller (2020). dplyr: A Grammar of Data
  Manipulation. R package version 1.0.2. https://CRAN.R-project.org/package=dplyr
  
- H. Wickham. ggplot2: Elegant Graphics for Data Analysis. Springer-Verlag New York, 2016.

- Charles Angelucci and Julia Cagé (2019). Newspapers in Times of Low Advertising Revenues. URL,   https://doi.org/10.1257/mic.20170306

- Yihui Xie (2016). bookdown: Authoring Books and Technical Documents with R Markdown. Chapman and Hall/CRC.
  ISBN 978-1138700109
  



